Hospital Information Technology and Physician Response

### 2022-03-18 Table Code/split stats.tex
Updates from Overleaf

\begin{table}[h]

\caption{Means by Age Sample}
\centering
\begin{tabular}[t]{lcc}
\toprule
Variable & Age $>$ 45 & Age $<=$ 45\\
\midrule
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Outcomes}}\\
\hspace{1em}Number of Hospitals Worked With & 1.54 & 1.38\\
\hspace{1em}Female & 0.27 & 0.41\\
\hspace{1em}Number of Systems Worked With & 1.33 & 1.23\\
\hspace{1em}Age & 51.83 & 37.79\\
\hspace{1em}Number of Patients & 2578.12 & 1359.17\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Treatment}}\\
\hspace{1em}Fraction of Hospitals with EHR & 0.51 & 0.55\\
\hspace{1em}Exposure to an EHR & 0.64 & 0.62\\
\hspace{1em}Exposure to an EHR (Low Integration) & 0.44 & 0.39\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Characteristics}}\\
\hspace{1em}Fraction Patients in Office & 0.36 & 0.19\\
\hspace{1em}Ever Retire & 0.02 & 0.02\\
\hspace{1em}Work in an Office & 0.66 & 0.37\\
\hspace{1em}Change Zip Codes & 0.07 & 0.11\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]

\caption{Means by Age Sample}
\centering
\begin{tabular}[t]{lccc}
\toprule
Variable & Age $>$ 60 & Age $<=$ 60 & Any Who Retire\\
\midrule
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Outcomes}}\\
\hspace{1em}Ever Retire & 0.01 & 0.01 & 1.00\\
\hspace{1em}Fraction Patients in Office & 0.44 & 0.27 & 0.15\\
\hspace{1em}Work in an Office & 0.79 & 0.52 & 0.33\\
\hspace{1em}Change Zip Codes & 0.06 & 0.09 & 0.08\\
\hspace{1em}Number of Patients & 3238.30 & 2028.23 & 554.53\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Treatment}}\\
\hspace{1em}Exposure to an EHR & 0.77 & 0.76 & 0.77\\
\hspace{1em}Exposure to an EHR (Low Integration) & 0.54 & 0.50 & 0.44\\
\hspace{1em}Fraction of Hospitals with EHR & 0.60 & 0.64 & 0.64\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Characteristics}}\\
\hspace{1em}Age & 61.06 & 44.06 & 48.29\\
\hspace{1em}Female & 0.15 & 0.35 & 0.39\\
\hspace{1em}Number of Hospitals Worked With & 1.67 & 1.53 & 1.35\\
\hspace{1em}Number of Systems Worked With & 1.41 & 1.33 & 1.19\\
\bottomrule
\end{tabular}
\end{table}
